Iterative construction of replicated designs based on Sobol' sequences

### 2016-06-10 crass/crassnew.tex
modifications section 4

We name by $A$ (resp. $B$) one of the two replicated designs constructed with the multiplicative (resp. additive) approach. We set the input space dimension $s$ equals to $6$. We also sampled $100$ designs of $A$ and $B$ whose average criteria are presented in Figure \ref{results.crit}. Each of the $100$ designs $A$ is independently randomized by applying Owen's scrambling. Each of the $100$ designs $B$ is sampled by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and by selecting the vectors $\ve_j$ following steps i) and ii). Design $A$ is refined until $\ell=12$, and design $B$ is constructed with an initial value $r=8$ and refined 15 times. The x-axis corresponds to the number of points $N$ of the design. THe y-axis corresponds to the value of the criterion. Logarithmic scale is used for both axis.

As expected, design $A$ performs the best and the estimated slope of the discrepancy curve ($-0.67$) falls within the expected range for Sobol' sequences \cite{Morokoff}. However, we observe that design $B$ outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $A$.

\begin{figure}
\caption{Log-log graph of averaged $L_2$ star discrepancy (left) and maximin (right) for designs $A$ and $B$ over $100$ repetitions.}
\label{results.crit}
\centering
\includegraphics[scale=0.4]{discrep.pdf}
\hspace*{0.1cm}
\includegraphics[scale=0.4]{mindist.pdf}
\end{figure}

>>>>

We name by design $A$ (resp. $B$) one of the two replicated designs constructed with the multiplicative (resp. additive) approach. We set the input space dimension $s$ equals to $6$. Design $A$ is refined until $\ell=12$, and design $B$ is constructed with an initial value $r=8$ and refined 15 times.  We construct $100$ designs $A$ and $B$ whose average criteria are presented in Figure \ref{results.crit}. Each of the $100$ designs $A$ is independently randomized by applying Owen's scrambling. Each of the $100$ designs $B$ is constructed by randomly selecting the matrix $L$ among the $2^{r(r-1)/2}$ choices and by selecting the vectors $\ve_j$ following steps i) and ii). We also represent  in Figure \ref{results.crit} the results obtained with a Latin Hypercube design with an equal number of points of design $B$. The x-axis corresponds to the number of points $N$ of the design. The y-axis corresponds to the value of the criterion. A logarithmic scale is used for both axis.

As expected, design $A$ performs the best and the estimated slope of the discrepancy curve ($-0.67$) falls within the expected range for Sobol' sequences \cite{Morokoff}. However, we observe that design $B$ outperforms a classic Latin Hypercube design for both criteria while allowing $15$ refinement steps from $2^8$ to $2^{12}$ points, instead of only $4$ steps for design $A$.
\begin{figure}
\caption{Log-log graph of averaged $L_2$ star discrepancy (left) and maximin (right) for designs $A$ and $B$ over $100$ repetitions.}
\label{results.crit}
\centering
\includegraphics[scale=0.4]{discrep.pdf}
\hspace*{0.1cm}
\includegraphics[scale=0.4]{mindist.pdf}
\end{figure}
